Centers and centralizers of higher enveloping algebras of Lie algebras

### 2020-09-10 draft.tex
fields

\begin{dfn}
Let $M$ be an $n$-dimensional manifold and let $\fg$ be an $L_\infty$ algebra. 
{\em Topological BF theory with its universal Neumann boundary condition} is the classical BV theory on $M \times \RR_{\geq 0}$ described by the following constructible sheaf $\cL$ of $L_\infty$ algebras:
\begin{itemize}
\item[(1)] 
The bulk theory is perturbative topological BF theory on $M \times \RR_{>0}$. 
That is, to an open set $U \subset M \times \RR_{>0}$ the theory is described by the $L_\infty$ algebra 
\[
\cL (U) = \Omega^{\bu} (U) \otimes \fg [1] \ltimes \Omega^{\bu} (U) \otimes \fg^* [n-3] .
\]
\item[(2)] 
To an open set $V \times [0,\epsilon)$, we assign the (abelian) $L_\infty$ algebra
\[
\cL (V \times [0,\epsilon)) = \Omega^{\bu} (V \times [0,\epsilon)) \otimes \fg^* [n-3] .
\]
\end{itemize}
\end{dfn}

@@

\begin{prp}
There is a quasi-isomorphism of constructible factorization algebras on $M \times \RR_{\geq 0}$:
\[
\bC_n (\fg) \xto{\simeq} \clies(\cL) .
\]
\end{prp}

\owen{$\PP_0$ algebras?}

>>>>

\begin{dfn}
Let $M$ be an $n$-dimensional manifold and let $\fg$ be an $L_\infty$ algebra. 
{\em Topological BF theory with its universal Neumann boundary condition} is the classical BV theory on $M \times \RR_{\geq 0}$ described by the following constructible sheaf $\cL$ of $L_\infty$ algebras:
\begin{itemize}
\item[(1)] 
The bulk theory is perturbative topological BF theory on $M \times \RR_{>0}$. 
That is, to an open set $U \subset M \times \RR_{>0}$ the theory is described by the $L_\infty$ algebra 
\[
\cL (U) = \Omega^{\bu} (U) \otimes \fg [1] \ltimes \Omega^{\bu} (U) \otimes \fg^* [n-3] .
\]
\item[(2)] 
To an open set $V \times [0,\epsilon)$, we assign the $L_\infty$ algebra
\[
\cL (V \times [0,\epsilon)) = \Omega^\bu (V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) \otimes \fg \ltimes \Omega^{\bu} (V \times [0,\epsilon)) \otimes \fg^* [n-3] .
\]
\end{itemize}
\end{dfn}

@@

\begin{prp}
There is a quasi-isomorphism of constructible $\PP_0$-factorization algebras on $M \times \RR_{\geq 0}$:
\[
\bC_n (\fg) \xto{\simeq} \clies(\cL) .
\]
\end{prp}
